---
title: "Assignment 2 part 1.5&1.6"
author: "Fangzhou Yang"
date: "10/12/2017"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Main

Firstly, we source all of the functions what we have saved in 1.4, and define variables:
```{r}
source("Source.R")
trueA <- 5  
trueB <- 0    
trueSd <- 10  
sampleSize <- 31 

x <- (-(sampleSize-1)/2):((sampleSize-1)/2)
y <-  trueA * x + trueB + rnorm(n=sampleSize,mean=0,sd=trueSd)
plot(x,y,main="Test Data")
```

Plot the graph of slope lokelihood:
```{r}
slopelikelihoods=lapply(seq(3, 7, by=.05), slopevalues )
plot (seq(3, 7, by=.05), slopelikelihoods , type="l", 
      xlab = "values of slope parameter a", ylab = "Log likelihood")
```

Set value to the variables as below and plot graphs of a,b and sd:
```{r}
startvalue = c(4,0,10) 
chain = run_metropolis_MCMC(startvalue, 10000)
burnIn = 5000
acceptance = 1-mean(duplicated(chain[-(1:burnIn),]))
fit_13(chain,burnIn,trueA,trueB,trueSd)
summary(lm(y~x))
```


Write the compare_outcomes function:
```{r}
compare_outcomes<-function(iteration){
  for(i in 1:10){
    a<-runif(1,min=0,max=10)
    b<-rnorm(1)
    sd<-runif(1,min=0,max=20)
    startvalue <- c(a,b,sd) 
    chain<- run_metropolis_MCMC(startvalue, iteration)  
    meana<-mean(chain[,1])
    sda<-sd(chain[,1])
    print(paste("mean is",meana, "sd is",sda))
  }
}

```


Test the compare_outcomes function use iteration = 1000,10000 and 100000.
```{r}
fit1 <- compare_outcomes(1000)
fit2 <- compare_outcomes(10000)
fit3 <- compare_outcomes(100000)
```


From the test, we can see that the mean is around 4.97, and as iteration goes bigger, the mean is getting stable. Therefore we'd like to use a larger iteration to get an accurate outcome, but I think the iteration is no need to be pretty big, since it is unnecesary and run slow.